\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Sampad Kumar Kar}} & Email: \href{mailto:}{sampaddavcspur2001@gmail.com}\\
  & \href{mailto:}{sampadk04@cmi.ac.in}\\
  \href{https://sampadk04.github.io}{Portfolio: ~sampadk04.github.io} & Mobile:~~~+91-797-8620-354 \\
  \href{https://github.com/sampadk04}{Github: ~~~github.com/sampadk04}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chennai Mathematical Institute}{Chennai, India}
      {M.Sc. - Computer Science; \textbf{GPA: 9.00}; \textit{\href{https://github.com/sampadk04/CV/blob/main/Transcripts/transcript_MCS202215_cmi.pdf}{transcript}}}{2022 - present}

    \resumeSubheading
      {Chennai Mathematical Institute}{Chennai, India}
      {B.Sc.(Hons.) - Mathematics and Computer Science;  \textbf{GPA: 8.82}; \textit{\href{https://github.com/sampadk04/CV/blob/main/Transcripts/transcript_BMC201944_cmi.pdf}{transcript}}}{2019 - 2022}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}

%-----------Experience-----------------
\section{Experience}
  \resumeSubHeadingListStart

\begin{comment}
    \resumeSubheading{Google Summer of Code - Submitty}{Remote}
    {Student Developer (Full-time)}{May 2019 - Sep 2019}
    \resumeItemListStart
        \resumeItem{Discussion Forum Upgrades}
          {Refactor forum for performance to handle large databases.}
          \resumeItem{REST API for Discussion Forum}
          {Symphony \& Twig based Forum parts converted to API-first interface.}
          \resumeItem{Ratchet PHP WebSocket}{Implemented a WebSocket for low-latency real time exchange of posts and thread updates.}
      \resumeItemListEnd
\end{comment}

\resumeSubheading{\href{https://www.michelin.in/}{Michelin}}{Pune (Hybrid), India}
{Data Science Intern}{Dec 2023 - May 2024}
\resumeItemListStart
    \resumeItem{Projects}
      {TyreScan, TyreSnap}
    \resumeItem{Contribution}
      {In TyreScan project, deployed end-to-end pipelines for verifying and extracting tyre attributes via web-scraping, given the EAN Code. In TyreSnap, developed a calibrated confidence scoring system post-object, label, and text detection pipeline, reflecting a more human-aligned confidence score.}
  \resumeItemListEnd

    \resumeSubheading{\href{https://www.bnymellon.com/}{BNY Mellon}}{Chennai, India}
    {Financial Modelling Intern (PPO)}{May 2023 - July 2023}
    \resumeItemListStart
        \resumeItem{Project}
          {Enhancing Short Term Cash Flow Model}
        \resumeItem{Contribution}
          {Improved BNY Mellon's STCF forecasting by introducing quantitative methods for identifying seasonal patterns, enhancing accuracy across LOBs and currencies. Conducted statistical tests and modeling to validate the quantitative framework, which was subsequently submitted to Risk for audit and adoption. \textit{\href{https://github.com/sampadk04/Internship_Reports/blob/main/BNY_Mellon/Enhancing_Short_Term_Cashflow-Internship_Report.pdf}{Report}}}
      \resumeItemListEnd

    \resumeSubheading{\href{https://www.trumpf.com/en_IN/}{Trumpf}}{Chennai, India}
    {Computer Vision Intern}{Nov 2022 - Apr 2023}
    \resumeItemListStart
        \resumeItem{Project}
          {Sheet Metal Part Identification}
        \resumeItem{Contribution}
          {Developed a deployable pipeline for sheet metal part identification, using transfer learning on pre-trained models to classify images into 10 predefined categories and output the corresponding CAD files. \textit{\href{https://github.com/sampadk04/Internship_Reports/blob/main/Trumpf_Metamation/Sheet_Metal_Part_Recognition-Internship_Report.pdf}{Report}}}
      \resumeItemListEnd

    \resumeSubheading{\href{https://www.launchpad.ai}{Launchpad.ai}}{Remote}
    {Machine Learning Intern}{July 2022 - Sep 2022}
    \resumeItemListStart
        \resumeItem{Project}
          {Fitness Activity Recognition (in collaboration with Nike)}
        \resumeItem{Contribution}
          {Collaborated with Cohort'23 to create a model for comparing trainee and expert fitness videos. Utilized 'Dynamic Time Warping' on coordinates extracted via 'Mediapipe Blazepose' to handle variations in camera angles. \textit{\href{https://github.com/sampadk04/Internship_Reports/blob/main/Launchpad/Fitness_Activity_Recognition-Final_Report.pdf}{Report}}}
      \resumeItemListEnd
    
    \resumeSubheading{\href{https://www.cheenta.com}{Cheenta}}{Remote}
    {Mathematics Instructor}{Oct 2019 - Apr 2022}
    \resumeItemListStart
        \resumeItem{Mathematics Olympiad Instructor}
          {Taught various courses for Indian National Mathematics Olympiads on various topics like Geometry, Number Theory, Algebra etc.}
      \resumeItemListEnd
    

\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{\href{https://sampadk04.github.io/post/}{Notable Projects}}
\resumeSubHeadingListStart

\begin{comment}
\resumeSubItem{Computer Vision - \href{https://sampadk04.github.io/post/project-9/}{Fitness Activity Recognition}}{(Internship Project): Used Google's MediaPipe Pose ML solution with BlazePose to analyze fitness demonstration videos for guided instructions to - 1) recognize classify the exercises on a per frame basis; 2) count the no. of repetitions, using Google RepNet; 3) use DTW (Dynamic Time Warping to compare the trainer videos (experts) to the trainee videos (learners) and output a score. \textit{\href{https://www.launchpad.ai/blog/fitness-activity-recognition-using-mediapipe-blazepose}{Blog}} \textit{\href{https://github.com/sampadk04/fitness-activity-recognition/blob/main/Report.pdf}{Report}} \textit{\href{https://github.com/sampadk04/fitness-activity-recognition}{GitHub}} (August '22)}
\vspace{2pt}
\end{comment}

\begin{comment}
\resumeSubItem{ToDo WebApp - \href{https://sampadk04.github.io/post/project-7/}{My ToDo WebApp}}{(Flask WebApp): A social ToDo app to keep track of group tasks. In this shared ToDo WebApp, everyone can view the public ToDo List and Add/Update/Delete the tasks. The Heroku deployed version of this app can be found \href{https://webappmytodo.herokuapp.com/}{here}. \textit{\href{https://github.com/sampadk04/myToDo}{GitHub}} (June '22)}
\vspace{2pt}
\end{comment}

\begin{comment}
\resumeSubItem{ANN - \href{https://sampadk04.github.io/post/project-0/}{Comparison of Regularization Techniques in DNNs}}{(Reading Project): Comparative research on several popular regularization techniques using real world weather dataset. Also tested this on their own test set, to validate the conclusions based on training and validation errors, to come up with the best regularization paradigm. \textit{\href{https://drive.google.com/file/d/1IdB25eOe6ux7u2mR4tHNifdWi-Pfh87G/view?usp=sharing}{Report}} (January '22)}
\vspace{2pt}
\end{comment}

\resumeSubItem{Clustering - \href{https://sampadk04.github.io/post/project-6/}{Fast Text based Clustering}}{Developed four clustering techniques, including two optimized versions of sklearn's KMeans and two novel techniques designed from scratch to efficiently cluster large datasets using 'Jaccard Similarity' as the metric. \textit{\href{https://github.com/sampadk04/Fast_Text_based_Clustering}{GitHub}} (April '22)}
\vspace{2pt}

\resumeSubItem{Computer Vision - \href{https://sampadk04.github.io/post/project-12/}{Facial Emotion Detector}}{Created a real-time facial expression detector using Deep Residual Networks upon the \textit{Kaggle Facial Expression Dataset}, with deployment for live webcam-based emotion recognition. \textit{\href{https://github.com/sampadk04/Facial_Emotion_Detector}{GitHub}} (Jan '23)}
\vspace{2pt}

\begin{comment}
\resumeSubItem{Reinforcement Learning - \href{https://sampadk04.github.io/post/project-8/}{Playing Super Mario Bros}}{(OpenAI Gym): A Reinforcement Learning implementation on the OpenAI Gym environment setup for Super Mario Bros using the PPO (Proximal Policy Optimization) Algorithm. \textit{\href{https://github.com/sampadk04/openai-super-mario-bros}{GitHub}} (Aug '22)}
\vspace{2pt}
\end{comment}

\resumeSubItem{Large Language Models - \href{https://sampadk04.github.io/post/project-14/}{Local GPT for Documents}}{Developed a local, internet-independent framework for querying and chatting with users' \textit{Private Documents} in natural language using LLMs, while also identifying document references from the knowlwedge base. \textit{\href{https://github.com/sampadk04/MyLocalGPT}{GitHub}} (Aug '22)}
\vspace{2pt}

\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------Teaching Assistant Experience-----------------
\section{TA Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading{\href{https://www.cmi.ac.in}{Chennai Mathematical Institute}}{Chennai, India}
    {Teaching Assistant}{Jan 2023 - present}
    \resumeItemListStart
        \resumeItem{\href{https://www.cmi.ac.in/~madhavan/courses/dmml2023/}{Data Mining and Machine Learning}}
          {Instructors: \href{https://www.cmi.ac.in/~madhavan/}{Prof. Madhavan Mukund}, \href{https://pranabendu.bitbucket.io}{Prof. Pranabendu Misra}}

        \resumeItem{\href{https://www.cmi.ac.in/~pranabendu/aml23/}{Advanced Machine Learning}}
          {Instructors: \href{https://pranabendu.bitbucket.io}{Prof. Pranabendu Misra}}

        \resumeItem{Natural Language Processing}
          {Instructors: \href{https://in.linkedin.com/in/ramaseshanr}{Prof. Ramaseshan Ramachandran}}
      \resumeItemListEnd

\begin{comment}
    \resumeSubheading{\href{https://saiuniversity.edu.in}{Sai University}}{Chennai, India}
    {Teaching Assistant}{Aug 2023 - present}
    \resumeItemListStart
        \resumeItem{Introduction to Cryptography}
          {Instructors: \href{https://sites.google.com/view/ksutar}{Prof. Kavita Sutar}}
      \resumeItemListEnd
\end{comment}
    

\resumeSubHeadingListEnd
\vspace{-5pt}

%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {Shriram Scholarship (Full Tution Fee Waiver and Stipend at CMI for Masters) - 2022 - present}
\vspace{-5pt}
\item {Shriram Scholarship (Full Tution Fee Waiver and Stipend at CMI for Bachelors) - 2019 - 2022}
\vspace{-5pt}
\item {NTSE Scholar, INMO Merit Awardee - 2017}
\vspace{-5pt}
\item {KVPY, RMO, NSEP, NSEA Qualifier - 2017-18}
\vspace{-5pt}
\item {JEE Advanced AIR \textbf{4062}, JEE Mains AIR \textbf{3042}  - 2019}

\end{description}
\vspace{-5pt}

%-----------Skills-----------------
\section{Technical Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~~~~~Python, R, Matlab C++, Java, Haskell}
	\resumeSubItem{ML Frameworks}{~NumPy, Pandas, Scikit, PyTorch, transformers, LangChain, NLTK, OpenCV, Matplotlib, Seaborn}

\resumeSubHeadingListEnd
\vspace{-5pt}






\begin{comment}
\vspace{-5pt}
%-----------Publications-----------------
\section{Publications}
\resumeSubHeadingListStart
\resumeSubItem{Book: Deep Learning on Web (Web Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Django, Python, AWS, GCP, Azure (November '18)}
\vspace{2pt}
\resumeSubItem{Book: Deep Learning on Mobile Devices (Flutter App Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Flutter, Android, Firebase, TensorFlow, Python, Dart (December '18)}
\resumeSubHeadingListEnd
\end{comment}




\begin{comment}
\vspace{-5pt}
%-----------Volunteer Experience-----------------
\section{Volunteer Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
    {Community Lead at Developer Student Clubs NSEC}{Kolkata, India}
    {Conducted online and offline technical \& soft-skills training impacting over 3000 students.}{Jan 2019 - Present}
\vspace{5pt}
    % \vspace{10pt}\textbf{\large{Community Experience}}
    \resumeSubheading
    {Event Organizer at Google Developers Group Kolkata}{Kolkata, India}
    {Organized events, conducted workshops and delivered workshops reaching over 7000 developers.}{Jan 2018 - Present}
\resumeSubHeadingListEnd
\end{comment}






\end{document}