\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Sampad Kumar Kar}} & Email: \href{mailto:}{sampaddavcspur2001@gmail.com}\\
  & \href{mailto:}{sampadk04@cmi.ac.in}\\
  \href{https://sampadk04.github.io}{Portfolio: sampadk04.github.io} & Mobile:~~~+91-797-8620-354 \\
  \href{https://github.com/sampadk04}{Github: ~~github.com/sampadk04} \\
  \href{https://www.linkedin.com/in/sampadk04/}{LinkedIn: ~~linkedin.com/in/sampadk04/}
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chennai Mathematical Institute}{Chennai, India}
      {M.Sc. - Computer Science}{2022 - present}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Notable Coursework:} Advanced Machine Learning, Reinforcement Learning, Mathematical Logic}}}
    \resumeSubheading
      {Chennai Mathematical Institute}{Chennai, India}
      {B.Sc.(Hons.) - Mathematics and Computer Science;  \textbf{GPA: 8.82}; \textit{\href{https://github.com/sampadk04/CV/blob/main/transcript_BMC201944_cmi.pdf}{transcript}}}{2019 - 2022}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Notable Coursework:} Calculus, Differential Equations, Probability Theory, Linear Algebra,Theoretical Foundations of ML, Data Mining and ML, Probability and Statistics with R, Linear Programming and Combinatorial Optimisation}}}
    \resumeSubheading
      {Indian Institute of Technology, Madras}{Chennai, India}
      {B.Sc. - Data Science;  \textbf{GPA: 9.2}; \textit{\href{https://github.com/sampadk04/CV/blob/main/transcript_21f1000353_iitm.pdf}{transcript}}}{2020 - Present}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Notable Coursework:} Programming and Data Structure with Python, ML Foundations, ML Techniques, ML Practice, Business Data Management, Tools for Data Science}}}
    \resumeSubHeadingListEnd
	    
\vspace{-5pt}

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{\href{https://sampadk04.github.io/post/}{Projects}}
\resumeSubHeadingListStart

\resumeSubItem{Computer Vision - \href{https://sampadk04.github.io/post/project-9/}{Fitness Activity Recognition}}{(Internship Project): Used Google's MediaPipe Pose ML solution with BlazePose to analyze fitness demonstration videos for guided instructions to - 1) recognize classify the exercises on a per frame basis; 2) count the no. of repetitions, using Google RepNet; 3) use DTW (Dynamic Time Warping to compare the trainer videos (experts) to the trainee videos (learners) and output a score. \textit{\href{https://www.launchpad.ai/blog/fitness-activity-recognition-using-mediapipe-blazepose}{Blog}} \textit{\href{https://github.com/sampadk04/fitness-activity-recognition/blob/main/Report.pdf}{Report}} \textit{\href{https://github.com/sampadk04/fitness-activity-recognition}{GitHub}} (August '22)}
\vspace{2pt}

\resumeSubItem{ToDo WebApp - \href{https://sampadk04.github.io/post/project-7/}{My ToDo WebApp}}{(Flask WebApp): A social ToDo app to keep track of group tasks. In this shared ToDo WebApp, everyone can view the public ToDo List and Add/Update/Delete the tasks. The Heroku deployed version of this app can be found \href{https://webappmytodo.herokuapp.com/}{here}. \textit{\href{https://github.com/sampadk04/myToDo}{GitHub}} (June '22)}
\vspace{2pt}

\resumeSubItem{ANN - \href{https://sampadk04.github.io/post/project-0/}{Comparison of Regularization Techniques in DNNs}}{(Reading Project): Comparative research on several popular regularization techniques using real world weather dataset. Also tested this on their own test set, to validate the conclusions based on training and validation errors, to come up with the best regularization paradigm. \textit{\href{https://drive.google.com/file/d/1IdB25eOe6ux7u2mR4tHNifdWi-Pfh87G/view?usp=sharing}{Report}} (January '22)}
\vspace{2pt}

\resumeSubItem{\href{https://sampadk04.github.io/post/project-6/}{Clustering - Fast Text based Clustering}}{Developed 4 clustering techniques, two of them based on built-in sklearn 'KMeans', and two new techniques coded from scratch to cluster bigger datasets, all using 'Jaccard Similarity' as metric. Optimised these algorithms to be able to cluster bigger datasets for further semi-supervised learnings. \textit{\href{https://github.com/sampadk04/Fast_Text_based_Clustering}{GitHub}} (April '22)}
\vspace{2pt}

\resumeSubItem{Reinforcement Learning - \href{https://sampadk04.github.io/post/project-8/}{Playing Super Mario Bros}}{(OpenAI Gym): A Reinforcement Learning implementation on the OpenAI Gym environment setup for Super Mario Bros using the PPO (Proximal Policy Optimization) Algorithm. \textit{\href{https://github.com/sampadk04/openai-super-mario-bros}{GitHub}} (August '22)}
\vspace{2pt}

\resumeSubHeadingListEnd
\vspace{-5pt}


%-----------Experience-----------------
\section{Experience}
  \resumeSubHeadingListStart

\begin{comment}
    \resumeSubheading{Google Summer of Code - Submitty}{Remote}
    {Student Developer (Full-time)}{May 2019 - Sep 2019}
    \resumeItemListStart
        \resumeItem{Discussion Forum Upgrades}
          {Refactor forum for performance to handle large databases.}
          \resumeItem{REST API for Discussion Forum}
          {Symphony \& Twig based Forum parts converted to API-first interface.}
          \resumeItem{Ratchet PHP WebSocket}{Implemented a WebSocket for low-latency real time exchange of posts and thread updates.}
      \resumeItemListEnd
\end{comment}
    
    \resumeSubheading{\href{https://www.launchpad.ai}{Launchpad.ai}}{Remote}
    {Machine Learning Intern}{July 2022 - Sep 2022}
    \resumeItemListStart
        \resumeItem{Project}
          {Worked with the Cohort'23 in the project \textbf{Fitness Activity Recognition} in collaboration with Nike to develop a generic model to identify and compare the videos of trainee with the expert.}
        \resumeItem{Contribution}
          {Developed algorithms using DTW (Dynamic Time Warping) to compare videos using the coordinates extracted via Mediapipe Blazepose, while making the comparison robust to difference in camera angles. \textit{\href{https://github.com/sampadk04/fitness-activity-recognition/blob/main/Report.pdf}{Report}}}
      \resumeItemListEnd
    
    \resumeSubheading{\href{https://www.cheenta.com}{Cheenta}}{Remote}
    {Mathematics Instructor (part-time)}{Oct 2019 - Apr 2022}
    \resumeItemListStart
        \resumeItem{Mathematics Olympiad Instructor}
          {Taught various courses for Indian National Mathematics Olympiads on various topics like Geometry, Number Theory, Algebra etc.}
      \resumeItemListEnd
    

\resumeSubHeadingListEnd
\vspace{-5pt}


%-----------Awards-----------------
\section{Honors and Awards}
\begin{description}[font=$\bullet$]
\item {Shriram Scholarship (Full Tution Fee Waiver and Stipend at CMI for Masters) - 2022 - present}
\vspace{-5pt}
\item {Shriram Scholarship (Full Tution Fee Waiver and Stipend at CMI for Bachelors) - 2019 - 2022}
\vspace{-5pt}
\item {NTSE Scholar - 2017}
\vspace{-5pt}
\item {INMO Merit Awardee - 2017 }
\vspace{-5pt}
\item {KVPY Qualifier - 2018}
\vspace{-5pt}
\item {NSEP, NSEA, RMO Qualifier - 2017-18}
\vspace{-5pt}
\item {JEE Advanced AIR \textbf{4062}, JEE Mains AIR \textbf{3042}  - 2019}

\end{description}
\vspace{-5pt}

%-----------Skills-----------------
\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~~~~~Python, R, Matlab C++, Java, Haskell}
	\resumeSubItem{ML Frameworks}{~NumPy, Pandas, Scikit, Tensorflow, NLTK, OpenCV, Matplotlib, Seaborn}
	\resumeSubItem{Web Dev}{~~~~~~~~~~~~HTML, CSS, Bootstrap, Javascript, Flask, Jinja2, SQLAlchemy}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~~~~~Git, PostgreSQL, \LaTeX, Excel, SQLite}
	\resumeSubItem{Platforms}{~~~~~~~~~~~Linux, Windows, Mac}
	\resumeSubItem{Soft Skills}{~~~~~~~~~~~Leadership, Event Management, Writing, Public Speaking, Time Management}

\resumeSubHeadingListEnd
\vspace{-5pt}






\begin{comment}
\vspace{-5pt}
%-----------Publications-----------------
\section{Publications}
\resumeSubHeadingListStart
\resumeSubItem{Book: Deep Learning on Web (Web Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Django, Python, AWS, GCP, Azure (November '18)}
\vspace{2pt}
\resumeSubItem{Book: Deep Learning on Mobile Devices (Flutter App Development, Deep Learning)}{Work in Progress book to be published by Packt Publishing in late 2019. Tech: Flutter, Android, Firebase, TensorFlow, Python, Dart (December '18)}
\resumeSubHeadingListEnd
\end{comment}




\begin{comment}
\vspace{-5pt}
%-----------Volunteer Experience-----------------
\section{Volunteer Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
    {Community Lead at Developer Student Clubs NSEC}{Kolkata, India}
    {Conducted online and offline technical \& soft-skills training impacting over 3000 students.}{Jan 2019 - Present}
\vspace{5pt}
    % \vspace{10pt}\textbf{\large{Community Experience}}
    \resumeSubheading
    {Event Organizer at Google Developers Group Kolkata}{Kolkata, India}
    {Organized events, conducted workshops and delivered workshops reaching over 7000 developers.}{Jan 2018 - Present}
\resumeSubHeadingListEnd
\end{comment}






\end{document}